### 2014-06-20 alex/2020.Rmd
fixed to not average PV

```{r avg, cache=TRUE, echo=FALSE}
avg_test = function(subj) {
  apply(student2012[, paste0("PV", 1:5, subj)], 1, mean)
}

@@

>>>>

```{r avg, cache=TRUE, echo=FALSE, eval=FALSE}
avg_test = function(subj) {
  apply(student2012[, paste0("PV", 1:5, subj)], 1, mean)
}

@@

```{r pv, cache=TRUE, echo=FALSE}
#choose which of the 5 PVs to use for each subject
student2012$math = as.numeric(student2012[, "PV1MATH"])
student2012$read = as.numeric(student2012[, "PV1READ"])
student2012$sci = as.numeric(student2012[, "PV1SCIE"])
```
